Ensembler: Enabling high-throughput molecular simulations at the superfamily scale

### 2016-01-15 manuscript-post-acceptance-submission/ensembler.tex
Minor edits to fix up manuscript before resubmission for production

\begin{codebox}[h]
\begin{adjustwidth}{-2.25in}{0in}
\footnotesize
\begin{Verbatim}[frame=single]
export KEY_MODELLER="Modeller license key"
conda config -add channels https://conda.anaconda.org/omnia
conda config -add channels https://conda.anaconda.org/salilab
conda install ensembler
\end{Verbatim}
\caption{{\bf Ensembler installation using {\tt conda} in a {\tt bash} shell. A license for MODELLER must first be obtained, and the license key should be used in place of the text {\tt "Modeller license key"}.}
}
\label{box:installation}
\end{adjustwidth}
\end{codebox}

@@

Sed non aliquet felis. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Mauris commodo justo ac dui pretium imperdiet. Sed suscipit iaculis mi at feugiat. Ut neque ipsum, luctus id lacus ut, laoreet scelerisque urna. Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed. Nam condimentum sem eget mollis euismod. Nullam dui urna, gravida venenatis dui et, tincidunt sodales ex. Nunc est dui, sodales sed mauris nec, auctor sagittis leo. Aliquam tincidunt, ex in facilisis elementum, libero lectus luctus est, non vulputate nisl augue at dolor. For more information, see \nameref{S1_Text}.

>>>>

\begin{codebox}[h]
\begin{adjustwidth}{-2.25in}{0in}
\footnotesize
\begin{Verbatim}[frame=single]
export KEY_MODELLER="Modeller license key"
conda config -add channels https://conda.anaconda.org/omnia
conda config -add channels https://conda.anaconda.org/salilab
conda install ensembler
\end{Verbatim}
\caption{{\bf Ensembler installation using {\tt conda} in a {\tt bash} shell. A license for MODELLER (free for academic use) must first be obtained, and the license key should be used in place of the text {\tt "Modeller license key"}.}
}
\label{box:installation}
\end{adjustwidth}
\end{codebox}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SUPPORTING INFORMATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
